{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-31 brainscopycut.tex
US spelling, and phrasing, for first section (introduction)
change seb's color
4.1 new scenario / 4.2 transition
Put back bibliography file deleted in earlier commit
We forgot no one

% To make comments, corrections, notes
\newcommand{\TB}[1]{\textcolor{blue}{#1}}
\newcommand{\new}[1]{\TB{#1}}
\newcommand{\tb}[1]{\textcolor{blue}{#1}}
\newcommand{\TG}[1]{\textcolor{MidnightBlue}{#1}}
\newcommand{\add}[1]{\TB{TOADD: #1}}
\newcommand{\ra}[1]{$\rightarrow$#1}
\newcommand{\replace}[2]{\sout{#1} \TB{#2}}
\newcommand{\rk}[1]{\TG{{\footnotesize {\bf[\emph{#1}]}}}}
\newcommand{\remark}[1]{\noindent\fbox{\parbox{.99\linewidth}{\TB{#1}}}}
\newcommand{\smallremark}[1]{\noindent\fbox{{\TB{#1}}}}
\newcommand{\marginnote}[1]{\marginpar{{\parbox{1.\linewidth}{\hrulefill\\\TB{\scriptsize \sf #1}}}}}
\newcommand{\cam}[1]{\textcolor{blue}{\small{[{\bf C:} }#1{]}}}

@@

We are warmly grateful to Ana Sofia Morais for her precious feedback and advice on this research, and to Jean-Pierre Nadal and Sharon Peperkamp \cam{forgot anyone?} for useful suggestions and comments.

\bibliographystyle{plainnat}
\bibliography{brainscopypaste.bib}

>>>>

% To make comments, corrections, notes
\newcommand{\TB}[1]{\textcolor{blue}{#1}}
\newcommand{\new}[1]{\TB{#1}}
\newcommand{\tb}[1]{\textcolor{blue}{#1}}
\newcommand{\TG}[1]{\textcolor{MidnightBlue}{#1}}
\newcommand{\add}[1]{\TB{TOADD: #1}}
\newcommand{\ra}[1]{$\rightarrow$#1}
\newcommand{\replace}[2]{\sout{#1} \TB{#2}}
\newcommand{\rk}[1]{\TG{{\footnotesize {\bf[\emph{#1}]}}}}
\newcommand{\remark}[1]{\noindent\fbox{\parbox{.99\linewidth}{\TB{#1}}}}
\newcommand{\smallremark}[1]{\noindent\fbox{{\TB{#1}}}}
\newcommand{\marginnote}[1]{\marginpar{{\parbox{1.\linewidth}{\hrulefill\\\TB{\scriptsize \sf #1}}}}}
\newcommand{\cam}[1]{\textcolor{blue}{\small{[{\bf C:} }#1{]}}}
\newcommand{\seb}[1]{\textcolor{blue}{[{\bf S:} #1{]}}}
\newcommand{\todo}{\fcolorbox{blue}{lightblue}{(...)}}
\definecolor{lightblue}{rgb}{.85,.85,1}

@@

We are warmly grateful to Ana Sofia Morais for her precious feedback and advice on this research, and to Jean-Pierre Nadal and Sharon Peperkamp \cam{forgot anyone?} \seb{nope, c'est bon} for useful suggestions and comments.

\bibliographystyle{plainnat}
\bibliography{brainscopycut.bib}
